Synthesising Complex Termination Arguments

### 2014-06-23 papers/termination/paper.tex
Some work on section 6

We present a reduction from program \emph{termination} to program \emph{synthesis}.
This reduction allows us to generate nonlinear, lexicographic ranking functions that
are correct for fixed-width machine arithmetic and floating-point arithmetic.
We use this reduction to build a semi-decision procedure for the termination
of fixed-width and floating-point arithmetic programs.
\end{abstract}

@@

\section{Combinatorics of Finite Termination}
In this section, we fix a model of computation, describe its semantics and
define the syntax of a language we will work over.

@@

\begin{corollary}
 Most terminating programs do not have linear ranking functions.
\end{corollary}

@@

\begin{theorem}
 Most functions are non-linear.
\end{theorem}

>>>>

We present a reduction from program \emph{termination} to program \emph{synthesis}.
This reduction allows us to generate nonlinear, lexicographic ranking functions that
are correct for fixed-width machine arithmetic and floating-point arithmetic.
We use this reduction to build a sound and complete procedure for the termination
of fixed-width and floating-point arithmetic programs.
\end{abstract}

@@

\iffalse
\section{Combinatorics of Finite Termination}
In this section, we fix a model of computation, describe its semantics and
define the syntax of a language we will work over.

@@

\begin{corollary}
 Most terminating programs do not have linear ranking functions.
\end{corollary}
\fi

@@

\begin{theorem}
Assuming a reasonable program encoding, the probability that a random program of length $l$ computes
a linear function is $O(2^{-l})$.
\end{theorem}
